RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface From a Distribution Perspective

### 2022-11-26 main.tex
:construction: Update table and contributions

\begin{document}
\title{RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface From a Distribution Perspective}
\author{
	\IEEEauthorblockN{
		Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
		and~Bruno~Clerckx,~\IEEEmembership{Fellow,~IEEE,}
		TODO
	}
	\thanks{
		The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx,TODO\}@imperial.ac.uk).
	}
}
\maketitle
% TODO why not use metamaterial? because high computational complexity and expectations of freedom (flexibility, reliability)
% * cooperative input design can be used for co-located RIScatter nodes.
% * hardward to modulate using RIS is already available.
% * RIScatter: enhance backscatter signal difference (suppress primary interference) or primary signal strength.
% ? For Backscatter community: why not adaptive channel coding? For RIS community: why not add randomness for modulation?
% ? RIS involves nonlinear circuits (e.g., diodes) and impedance design (i.e., perfect mismatching) is tricky for continuous phase shift; discrete candidate set is preferred (2-3 bits optimal)
% * Redefine RIS using book
% x Using RIS to encode is not very interesting as controller is anyway usable
% * Wi-Fi sampling rate 20 MHz (symbol period 50 nS), RFID symbol rate/load-switching speed 100s KHz to 10s MHz [Backscatter Communication], fast load-switching speed is key for high data rate - symbol ratio is not very large
% * Beamforming can cancel direct interference to avoid the collapse of noncoherent energy detection and enlarge energy gap.
% ? [Reconfigurable Intelligent Surface-Assisted Ambient Backscatter Communication Experimental Assessment]the authors of [5] show that, even in line-of-sight (LOS), the interferences and the desired signal can combine in such a way that the received signals at the reader side in the two states are close in power and only differ by their phases
% TODO Input probability distribution for discrete-value reflection (backscatter), constellation design for continue-value reflection (RIS)
% * channel coding: non-adaptive (line-coding) or adaptive (DMC)
% ? [Turbocharging] Since averaging must be done over a significant period of time to smooth out the variation in the TV transmissions, averaging does not allow rates much higher than 10 kbps [24].
% ? [mu-code]: use multiple Rxs for noncoherent direct interference cancellation (instead of receive diversity)
% * backscatter modulation <-> passive beamforming; add adaptive channel coding over (NRZ) line coding.
% ? semicoherent: known CSI, unknown primary/backscatter symbols
% * initialization, convergence, base 2 in simulation
% * SR analysis can achieve large rate at the cost of large N; RIScatter can achieve slightly lower rate at the same N, but also preserves primary performance for smaller N
% TODO tradeoff between primary (RIScatter, no SIC) and backscatter (SR, SIC)
% * SR assume very large N for primary rate analysis. However, in such cases SIC is questionable as energy detection over received signal as BBC is already good enough and noncoherent detection can also achieve reasonable performance?
% x when primary symbols are determined, optimal input distribution at high backscatter SNR is equiprobable for any detection (signal/energy)
% ? Channel estimation error, coordination issues

% * add table row: adaptive to information source/csi/link weights
% * explain link weights
% * add table row: distributions
% * table to sentences
% * add primary and backscatter flows to illustrations
% ! discuss table and add challenges in contribution 1
% ! transition challenges (distribution and constellation-adaptive) to contribution 2, 3
% * think RIScatter applications (use Rui's slides)

\begin{abstract}
	% \gls{bc} nodes harvest energy from and modulate information over an external electromagnetic wave by manipulating the magnitude, phase, and/or frequency of the scattered signal.
	% \gls{sr} incorporates a passive scatter node into existing radio networks to create additional propagation path and ride its own information towards the cooperative receiver.
	% \gls{ris} is a programmable reflector array that adapts the phase shift response to enhance or suppress signal strength in specific directions.
	\gls{bc} nodes harvest energy from and modulate information over an external electromagnetic wave.
	\gls{ris} adapts its phase shift response to enhance or suppress equivalent channel strength in specific directions.
	In this paper, we show how both seemingly different technologies and their derivatives can be unified to leverage their benefits simultaneously into a single architecture called RIScatter.
	Envisioned as a next-generation communication protocol, RIScatter consists of multiple dispersed or co-located scatter nodes whose reflection states can be adapted to partially engineer the equivalent channel of the existing link and partially modulate their own information onto the scattered wave.
	This contrasts with \gls{bc} (resp. \gls{ris}) where the reflection pattern is exclusively a function of the information symbol (resp. \gls{csi}).
	The key principle in RIScatter is to render the probability distribution of reflection states as a joint function of the information source, \gls{csi}, and \gls{qos} of both coexisting links.
	This enables RISscatter to softly bridge, generalize, and outperform \gls{bc} and \gls{ris}; boil down to either under specific input distribution; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
	For a single-user multi-node RIScatter network, we characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at the nodes, the active beamforming at the \gls{ap}, and the backscatter detection regions at the user.
	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming via smart input distribution design, and the proposed practical receiver effectively accommodates the double modulation and signal difference in active-passive coexisting networks.
\end{abstract}

@@

\begin{section}{Introduction}
	\begin{subsection}{Fundamentals}
		\IEEEPARstart{F}{uture} wireless network is envisioned to provide high throughput, uniform coverage, pervasive connectivity, heterogeneous control, and cognitive intelligence for trillions of portable devices.
		As a mature low-power communication technique, \gls{bc} separates a conventional transmitter into a \gls{rf} carrier emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
		In particular, the node harvests energy from impinging wave and embeds information over scattered signal, while the backscatter reader can be either co-located or separated with the carrier emitter, known as \gls{mbc} and \gls{bbc} in Fig. \subref*{fg:mbc} and \subref*{fg:bbc}, respectively.
		Its applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and passive sensor network \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized in the era of \gls{ioe}.
		However, conventional \gls{bc} nodes only respond when externally inquired by a nearby reader.
		% \cite{Liu2013b} proposed an \gls{ambc} system in Fig. \subref*{fg:ambc}, where battery-free nodes recycle ambient signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connection in between.
		\gls{ambc} was then proposed in \cite{Liu2013b} where battery-free nodes recycle ambient signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connection in between.
		As shown in Fig. \subref*{fg:ambc}, it eliminates the need of dedicated power supply, carrier emitter and frequency spectrum, but is subject to the strong direct-link interference.
		To tackle this, \cite{Yang2018} proposed cooperative \gls{ambc} where both primary (legacy) and backscatter links are decoded by the same receiver under various detection schemes.
		% The concept of cooperative \gls{ambc} was further refined as \gls{sr} in Fig. \subref*{fg:sr} that cognitively incorporates \gls{ambc} with existing systems \cite{Liang2020}.
		The concept was further refined as \gls{sr} illustrated in Fig. \subref*{fg:sr} that cognitively incorporates \gls{ambc} with existing systems \cite{Liang2020}.
		% In a \gls{sr} system, the active transmitter generates \gls{rf} wave carrying primary information, the passive node creates extra primary propagation path and superimposes its own message on the scattered signal, while the cooperative receiver jointly or sequentially decodes both links.
		In a \gls{sr} system, the active transmitter generates \gls{rf} wave carrying primary information, the passive node provides extra propagation path and ride its information over scattered signal, while the cooperative receiver jointly or sequentially decodes both links.
		Those \gls{bc} applications employ scatter nodes as pure information sources, and the primary link (if it exists) is indeed influenced by the randomness of backscatter modulation.
		On the other hand, \gls{ris} is a smart planar signal reflector that consists of numerous compact passive elements with adjustable amplitude and phase responses.
		The reflection pattern is deterministic over time that can be adaptively optimized and coordinated in real time.
		\gls{ris} recycles and redistributes the surrounding \gls{rf} waves to customize the wireless propagation environment for signal enhancement, interference suppression, scattering enrichment and non-line-of-sight bypassing \cite{Wu2021b}.

		A comparison of different scattering applications is summarized in Table \ref{tb:scattering_applications}.

		\begin{figure}[!t]
			\centering
			\subfloat[\gls{mbc}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/mbc.tex}
				}
				\label{fg:mbc}
			}
			\subfloat[\gls{bbc}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/bbc.tex}
				}
				\label{fg:bbc}
			}
			\\
			\subfloat[\gls{ambc}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/ambc.tex}
				}
				\label{fg:ambc}
			}
			\subfloat[\gls{sr}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/sr.tex}
				}
				\label{fg:sr}
			}
			\\
			\subfloat[\gls{ris}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/ris.tex}
				}
				\label{fg:ris}
			}
			\subfloat[RIScatter]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/riscatter.tex}
				}
				\label{fg:riscatter}
			}
			\caption{
				Illustration of scattering applications.
				The blue paths constitute the primary link while the magenta/green paths denote the backscatter link.
			}
			\label{fg:scatter_illustration}
		\end{figure}
	\end{subsection}

	\begin{table*}[!t]
		\caption{Comparison of Scattering Applications}
		\label{tb:scattering_applications}
		\rowcolors{2}{gray!25}{white}
		\renewcommand{\arraystretch}{1.5}
		\begin{tabularx}{\textwidth}{CCCCCC}
			\toprule
			\hiderowcolors
			                                 & \gls{mbc}/\gls{bbc} & \gls{ambc}         & \gls{sr}                                      & \gls{ris}           & RIScatter                                                               \\ \midrule
			\showrowcolors
			Coexisting link(s)               & 1                   & 2 (competitive)    & 2 (collaborative)                             & 1                   & 2 (collaborative)                                                       \\
			Backscatter modulation           & Yes                 & Yes                & Yes                                           & No                  & Yes                                                                     \\
			Scatterer impact on primary link & ---                 & Interference       & Channel uncertainty                           & Passive beamforming & Dynamic passive beamforming                                             \\
			Cooperative transmission(s)      & ---                 & No                 & Primary transmitter (active beamforming)      & ---                 & Primary transmitter and scatter nodes                                   \\
			Co-located receiver              & ---                 & No                 & Usually \gls{sic} from primary to backscatter & ---                 & No \gls{sic}, backscatter detection as part of primary channel training \\
			Primary detection                & ---                 & Semi-coherent      & Semi-coherent                                 & Coherent            & Coherent                                                                \\
			Backscatter detection            & Coherent            & Semi-coherent      & Coherent                                      & ---                 & Semi-coherent                                                           \\
			Reflection pattern depends on    & Information source  & Information source & Information source                            & \gls{csi}           & Information source, \gls{csi}, and \gls{qos}                            \\
			Input distribution               & Equiprobable        & Equiprobable       & Equiprobable or Gaussian                      & Degenerate          & Flexible                                                                \\
			Load-switching speed             & Fast                & Fast or slow       & Very slow                                     & Quasi-static        & Flexible                                                                \\ \bottomrule
		\end{tabularx}
	\end{table*}

@@

		During primary decoding, the backscatter randomness can be modelled as either interference or channel uncertainty, depending on the ratio $N$ of primary sampling rate over backscatter load-switching speed\footnote{For state-of-the-art low-power \gls{rfid} tags, the load-switching speed usually varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, suggesting a typical $N$ between \num{10} and \num{1000}.}.

@@

		Conventional \gls{ris} design with fixed reflection coefficients during each channel block has been extensively studied in communication, sensing, and power literatures \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
		On the other hand, dynamic \gls{ris} with independent reflection patterns at different transmission phases has gained recent attentions in multi-user and multi-purpose wireless networks.
		The concept was first proposed in \cite{Yang2020} to fine-tune the \gls{ofdm} resource blocks, then extended to the downlink power and uplink information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
		It introduces artificial channel diversity and enables flexible resource allocation, but misses the opportunity to encode message at the \gls{ris}.
		% \gls{ris} can also be used as a transmitter when placed in the near field of a carrier emitter, and prototypes for \gls{psk} and \gls{qam} have been implemented in \cite{Tang2019a,Dai2020a}.
		When placed in the near field of a carrier emitter, \gls{ris} can also be used as a transmitter, and prototypes for \gls{psk} and \gls{qam} have been implemented in \cite{Tang2019a,Dai2020a}.
		From an information-theoretic perspective, \cite{Karasik2020} reported that using \gls{ris} as a naive passive beamformer to maximize the \gls{snr} is generally rate-suboptimal for finite input constellations.
		Instead, the capacity of \gls{ris}-aided channel is achieved by joint transmitter-\gls{ris} encoding, and multiplication coding with \gls{sic} decoding (i.e., \gls{sic}-based \gls{sr}) can outperform passive beamforming at high \gls{snr}.
		It inspired \gls{ris}-empowered \gls{bc} \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to combine passive beamforming and backscatter modulation in the overall reflection pattern.
		In particular, \emph{symbol level precoding} maps the information symbols to the optimized \gls{ris} coefficient sets \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes the information symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between the reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} employs dedicated reflection elements (resp. information elements) for passive beamforming (resp. backscatter modulation) \cite{Hu2021a}.
		% Those smart passive reflect elements/scatter nodes can recycle electromagnetic wave on the air to boost wireless channels and establish new connections, but incurs advanced hardware architecture and high optimization complexity.
		% Those \gls{ris}-empowered \gls{bc} can recycle electromagnetic wave on the air to simultaneously boost wireless channels and establish new connections, but the reflect elements or scatter nodes incurs advanced hardware architecture and high optimization complexity.
		Those \gls{ris}-empowered \gls{bc} designs can recycle \gls{rf} wave on the air and employ scattered paths to boost wireless channels and establish new connections, but incurs advanced hardware architecture and high optimization complexity.

		% the reflect elements or scatter nodes incurs advanced hardware architecture and high optimization complexity.
		% For backscatter information sources,
		% Besides,
		% Relevant literatures also consider either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} for backscatter information sources.
		% The former is impractical for passive backscatter devices while the latter does not fully exploit \gls{csi} and signal characteristics.
	\end{subsection}

@@

		\emph{First,} we propose RIScatter as a novel scatter protocol that unifies \gls{bc} and \gls{ris} from a distribution perspective.
		As shown in Fig. \subref*{fg:riscatter}, the passive RIScatter node rides over an active transmission and controls the scattered wave to
		partially engineer the wireless channel and partially modulate its own information.
		This is accomplished by incorporating both the \gls{csi} and \gls{qos} into the reflection state distribution design.
		As such, RIScatter can generalize \gls{bc} (uniform distribution) and \gls{ris} (degenerate distribution) to create a tradeoff between backscatter modulation and passive beamforming.
		This is the first paper to associate \gls{bc} and \gls{ris} from a distribution perspective.
		% heterogeneous traffic control and universal hardware design

		% I think you need to reemphasize what is the abstract and explain it further in light of the general observations you have drawn from the related works
		% IScatter design compared to backcom and RIS. How to tackle those challenges would then be explained in the subsequent contributions.

		\emph{Second,} we propose a practical receiver that accommodates the double modulation and signal difference in active-passive coexisting networks.
		Since the primary and backscatter messages are superimposed by multiplication coding and the backscatter symbol is typically longer than primary, the scattered signals from RIScatter nodes can be treated as multipath components during primary decoding, and the primary symbols can be viewed as a spreading code during backscatter decoding.
		Conventional sequential primary-backscatter decoder eliminates primary interference by \gls{sic} at each primary block, while our sequential backscatter-primary detector semi-coherently decodes RIScatter nodes from the received energy, re-encodes to recover exact reflection patterns, and models the deterministic multipath within primary equivalent channel as dynamic passive beamforming at each backscatter block.
		It enables backscatter modulation and dynamic passive beamforming at much lower operational complexity, and is suitable for scatter nodes with various load-switching speeds.

>>>>

\begin{document}
\title{RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface From a Distribution Perspective}
\author{
	\IEEEauthorblockN{
		Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
		and~Bruno~Clerckx,~\IEEEmembership{Fellow,~IEEE}
	}
	\thanks{
		The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx\}@imperial.ac.uk).
	}
}
\maketitle
% TODO why not use metamaterial? because high computational complexity and expectations of freedom (flexibility, reliability)
% * cooperative input design can be used for co-located RIScatter nodes.
% * hardward to modulate using RIS is already available.
% * RIScatter: enhance backscatter signal difference (suppress primary interference) or primary signal strength.
% ? For Backscatter community: why not adaptive channel coding? For RIS community: why not add randomness for modulation?
% ? RIS involves nonlinear circuits (e.g., diodes) and impedance design (i.e., perfect mismatching) is tricky for continuous phase shift; discrete candidate set is preferred (2-3 bits optimal)
% * Redefine RIS using book
% x Using RIS to encode is not very interesting as controller is anyway usable
% * Wi-Fi sampling rate 20 MHz (symbol period 50 nS), RFID symbol rate/load-switching speed 100s KHz to 10s MHz [Backscatter Communication], fast load-switching speed is key for high data rate - symbol ratio is not very large
% * Beamforming can cancel direct interference to avoid the collapse of noncoherent energy detection and enlarge energy gap.
% ? [Reconfigurable Intelligent Surface-Assisted Ambient Backscatter Communication Experimental Assessment]the authors of [5] show that, even in line-of-sight (LOS), the interferences and the desired signal can combine in such a way that the received signals at the reader side in the two states are close in power and only differ by their phases
% TODO Input probability distribution for discrete-value reflection (backscatter), constellation design for continue-value reflection (RIS)
% * channel coding: non-adaptive (line-coding) or adaptive (DMC)
% ? [Turbocharging] Since averaging must be done over a significant period of time to smooth out the variation in the TV transmissions, averaging does not allow rates much higher than 10 kbps [24].
% ? [mu-code]: use multiple Rxs for noncoherent direct interference cancellation (instead of receive diversity)
% * backscatter modulation <-> passive beamforming; add adaptive channel coding over (NRZ) line coding.
% ? semicoherent: known CSI, unknown primary/backscatter symbols
% * initialization, convergence, base 2 in simulation
% * SR analysis can achieve large rate at the cost of large N; RIScatter can achieve slightly lower rate at the same N, but also preserves primary performance for smaller N
% TODO tradeoff between primary (RIScatter, no SIC) and backscatter (SR, SIC)
% * SR assume very large N for primary rate analysis. However, in such cases SIC is questionable as energy detection over received signal as BBC is already good enough and noncoherent detection can also achieve reasonable performance?
% x when primary symbols are determined, optimal input distribution at high backscatter SNR is equiprobable for any detection (signal/energy)
% ? Channel estimation error, coordination issues

% * add table row: adaptive to information source/csi/link weights
% * explain link weights
% * add table row: distributions
% * table to sentences
% * add primary and backscatter flows to illustrations
% * discuss table and add challenges in contribution 1
% * transition challenges (distribution and constellation-adaptive) to contribution 2, 3
% * think RIScatter applications (use Rui's slides)

\begin{abstract}
	% \gls{bc} nodes harvest energy from and modulate information over an external electromagnetic wave by manipulating the magnitude, phase, and/or frequency of the scattered signal.
	% \gls{sr} incorporates a passive scatter node into existing radio networks to create additional propagation path and ride its own information towards the cooperative receiver.
	% \gls{ris} is a programmable reflector array that adapts the phase shift response to enhance or suppress signal strength in specific directions.
	\gls{bc} nodes harvest energy from and modulate information over an external electromagnetic wave.
	\gls{ris} adapts its phase shift response to enhance or suppress equivalent channel strength in specific directions.
	In this paper, we show how both seemingly different technologies and their derivatives can be unified to leverage their benefits simultaneously into a single architecture called RIScatter.
	Envisioned as a next-generation communication protocol, RIScatter consists of multiple dispersed or co-located scatter nodes whose reflection states can be adapted to partially engineer the equivalent channel of the existing link and partially modulate their own information onto the scattered wave.
	This contrasts with \gls{bc} (resp. \gls{ris}) where the reflection pattern is exclusively a function of the information symbol (resp. \gls{csi}).
	The key principle in RIScatter is to render the probability distribution of reflection states as a joint function of the information source, \gls{csi}, and \gls{qos} of both coexisting links.
	This enables RISscatter to softly bridge, generalize, and outperform \gls{bc} and \gls{ris}; boil down to either under specific input distribution; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
	For a single-user multi-node RIScatter network, we characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at the nodes, the active beamforming at the \gls{ap}, and the backscatter detection regions at the user.
	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming via smart input distribution design, and the tailored receiver effectively accommodates the double modulation and signal difference in active-passive coexisting networks without \gls{sic}.
\end{abstract}

@@

\begin{section}{Introduction}
	\begin{subsection}{Fundamentals}
		\IEEEPARstart{F}{uture} wireless network is envisioned to provide high throughput, uniform coverage, pervasive connectivity, heterogeneous control, and cognitive intelligence for trillions of portable devices.
		As a mature low-power communication technique, \gls{bc} separates a conventional transmitter into a \gls{rf} carrier emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
		In particular, the node harvests energy from impinging wave and embeds information over scattered signal, while the backscatter reader can be either co-located or separated with the carrier emitter, known as \gls{mbc} and \gls{bbc} in Fig. \subref*{fg:mbc} and \subref*{fg:bbc}, respectively.
		Its applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and passive sensor network \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized in the era of \gls{ioe}.
		However, conventional \gls{bc} nodes only respond when externally inquired by a nearby reader.
		\gls{ambc} was then proposed in \cite{Liu2013b} where battery-free nodes recycle ambient signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connection in between.
		As shown in Fig. \subref*{fg:ambc}, it eliminates the need of dedicated power supply, carrier emitter and frequency spectrum, but is subject to the strong direct-link interference.
		To tackle this, \cite{Yang2018} proposed cooperative \gls{ambc} where both primary (legacy) and backscatter links are decoded by the same receiver under various detection schemes.
		The concept was further refined as \gls{sr} illustrated in Fig. \subref*{fg:sr} that cognitively incorporates \gls{ambc} with existing systems \cite{Liang2020}.
		In a \gls{sr} system, the active transmitter generates \gls{rf} wave carrying primary information, the passive node provides extra propagation path and ride its information over scattered signal, while the cooperative receiver jointly or sequentially decodes both links.
		Those \gls{bc} applications employ scatter nodes as pure information sources, and the active transmission (if it exists) is indeed influenced by the randomness of backscatter modulation.
		On the other hand, \gls{ris} is a smart planar signal reflector that consists of numerous compact passive elements with adjustable amplitude and phase responses.
		The reflection pattern is deterministic over time that can be adaptively optimized and coordinated in real time.
		\gls{ris} recycles and redistributes the surrounding \gls{rf} waves to customize the wireless propagation environment for signal enhancement, interference suppression, scattering enrichment and non-line-of-sight bypassing \cite{Wu2021b}.

		Depending on the number of coexisting links, those scattering applications are divided into two categories that involve either active or passive transmission, or both active and passive transmissions.
		The corresponding information flows are illustrated in Fig. \ref{fg:scatter_illustration}.
		In \gls{mbc}/\gls{bbc} (resp. \gls{ris}), the passive device modulates information (resp. enhances propagation) while the active device generates carrier wave (resp. modulated signal).
		There is only the backscatter (resp. primary) link and the detection can be coherent.
		On the other hand, \gls{ambc} and \gls{sr} involve both links simultaneously, but the relationship in between is different.
		For \gls{ambc}, the primary link does not need to be aware of the backscatter link and both links are interfering each other.
		For \gls{sr}, both links are decoded by a co-located receiver, and cooperative transmission and reception become possible.
		A comparison of different scattering applications is summarized in Table \ref{tb:scattering_applications}.

		\begin{figure}[!t]
			\centering
			\subfloat[\gls{mbc}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/mbc.tex}
				}
				\label{fg:mbc}
			}
			\subfloat[\gls{bbc}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/bbc.tex}
				}
				\label{fg:bbc}
			}
			\\
			\subfloat[\gls{ambc}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/ambc.tex}
				}
				\label{fg:ambc}
			}
			\subfloat[\gls{sr}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/sr.tex}
				}
				\label{fg:sr}
			}
			\\
			\subfloat[\gls{ris}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/ris.tex}
				}
				\label{fg:ris}
			}
			\subfloat[RIScatter]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/riscatter.tex}
				}
				\label{fg:riscatter}
			}
			\caption{
				Illustration of scattering applications.
				For each, the blue flow(s) constitute the primary link while the magenta/green flow denotes the backscatter link.
			}
			\label{fg:scatter_illustration}
		\end{figure}
	\end{subsection}

	\begin{table*}[!t]
		\caption{Comparison of Scattering Applications}
		\label{tb:scattering_applications}
		\rowcolors{2}{gray!25}{white}
		\renewcommand{\arraystretch}{1.5}
		\begin{tabularx}{\textwidth}{CCCCCC}
			\toprule
			\hiderowcolors
			                                        & \gls{mbc}/\gls{bbc} & \gls{ambc}         & \gls{sr}                                      & \gls{ris}           & RIScatter                                                               \\ \midrule
			\showrowcolors
			Coexisting link(s)                      & 1                   & 2 (competitive)    & 2 (collaborative)                             & 1                   & 2 (collaborative)                                                       \\
			Primary/Backscatter modulation          & No/Yes              & Yes/Yes            & Yes/Yes                                       & Yes/No              & Yes/Yes                                                                 \\
			Primary impact on backscatter detection & Carrier             & Interference       & Spreading code                                & ---                 & Energy uncertainty                                                      \\
			Scatterer impact on primary detection   & ---                 & Interference       & Channel uncertainty                           & Passive beamforming & Dynamic passive beamforming                                             \\
			Cooperative transmission(s)             & ---                 & No                 & Primary transmitter (active beamforming)      & ---                 & Primary transmitter and scatter nodes                                   \\
			Co-located receiver                     & ---                 & No                 & Usually \gls{sic} from primary to backscatter & ---                 & No \gls{sic}, backscatter detection as part of primary channel training \\
			Primary detection                       & ---                 & Semi-coherent      & Semi-coherent                                 & Coherent            & Coherent                                                                \\
			Backscatter detection                   & Coherent            & Semi-coherent      & Coherent                                      & ---                 & Semi-coherent                                                           \\
			Reflection pattern depends on           & Information source  & Information source & Information source                            & \gls{csi}           & Information source, \gls{csi}, and \gls{qos}                            \\
			Input distribution                      & Equiprobable        & Equiprobable       & Equiprobable or Gaussian                      & Degenerate          & Flexible                                                                \\
			Load-switching speed                    & Fast                & Fast or slow       & Very slow                                     & Quasi-static        & Flexible                                                                \\ \bottomrule
		\end{tabularx}
	\end{table*}

@@

		During primary decoding, the backscatter randomness can be modelled as either interference or channel uncertainty, depending on the ratio $N$ of primary sampling rate over backscatter load-switching speed\footnote{For state-of-the-art low-power \gls{rfid} tags, the load-switching speed usually varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical $N$ between \num{10} and \num{1000}.}.

@@

		Conventional \gls{ris} design with fixed reflection coefficients during each channel block has been extensively studied in communication, sensing, and power literatures \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
		On the other hand, dynamic \gls{ris} with independent reflection patterns at different transmission phases has gained recent attentions in multi-user and multi-purpose wireless networks.
		The concept was first proposed in \cite{Yang2020} to fine-tune the \gls{ofdm} resource blocks, then extended to the downlink power and uplink information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
		It introduces artificial channel diversity and enables flexible resource allocation, but misses the opportunity to encode message at the \gls{ris}.
		% \gls{ris} can also be used as a transmitter when placed in the near field of a carrier emitter, and prototypes for \gls{psk} and \gls{qam} have been implemented in \cite{Tang2019a,Dai2020a}.
		When placed in the near field of a carrier emitter, \gls{ris} can also be used as a transmitter, and prototypes for \gls{psk} and \gls{qam} have been implemented in \cite{Tang2019a,Dai2020a}.
		From an information-theoretic perspective, \cite{Karasik2020} reported that using \gls{ris} as a naive passive beamformer to maximize the \gls{snr} is generally rate-suboptimal for finite input constellations.
		Instead, the capacity of \gls{ris}-aided channel is achieved by joint transmitter-\gls{ris} encoding, and multiplication coding with \gls{sic} decoding (i.e., \gls{sic}-based \gls{sr}) can outperform passive beamforming at high \gls{snr}.
		It inspired \gls{ris}-empowered \gls{bc} \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to combine passive beamforming and backscatter modulation in the overall reflection pattern.
		In particular, \emph{symbol level precoding} maps the information symbols to the optimized \gls{ris} coefficient sets \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes the information symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between the reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} employs dedicated reflection elements (resp. information elements) for passive beamforming (resp. backscatter modulation) \cite{Hu2021a}.
		% Those smart passive reflect elements/scatter nodes can recycle electromagnetic wave on the air to boost wireless channels and establish new connections, but incurs advanced hardware architecture and high optimization complexity.
		% Those \gls{ris}-empowered \gls{bc} can recycle electromagnetic wave on the air to simultaneously boost wireless channels and establish new connections, but the reflect elements or scatter nodes incurs advanced hardware architecture and high optimization complexity.
		Those \gls{ris}-empowered \gls{bc} designs can recycle \gls{rf} wave on the air and employ scattered paths to boost wireless channels and establish new connections, but incurs advanced hardware architecture and high optimization complexity.
		Relevant literatures also consider either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} for backscatter information sources.
		The former is impractical for passive backscatter devices while the latter does not fully exploit \gls{csi} and signal characteristics.
	\end{subsection}

@@

		% \emph{First,} we propose RIScatter as a novel scatter protocol that unifies \gls{bc} and \gls{ris} from a distribution perspective.
		% As shown in Fig. \subref*{fg:riscatter}, the passive RIScatter node rides over an active transmission and controls the scattered wave to
		% partially engineer the wireless channel and partially modulate its own information.
		% This is accomplished by incorporating both the \gls{csi} and \gls{qos} into the reflection state distribution design.
		% As such, RIScatter can generalize \gls{bc} (uniform distribution) and \gls{ris} (degenerate distribution) to create a tradeoff between backscatter modulation and passive beamforming.
		% This is the first paper to associate \gls{bc} and \gls{ris} from a distribution perspective.

		\emph{First,} we propose RIScatter as a novel scatter protocol that unifies \gls{bc} and \gls{ris} from a distribution perspective.
		As shown in Fig. \subref*{fg:riscatter}, the passive RIScatter node rides over an active transmission and controls the scattered wave to simultaneously engineer the wireless channel and modulate its own information, while a co-located receiver decodes both primary and backscatter links in a cooperative manner.
		The reflection pattern of each RIScatter node is no longer fully random like \gls{bc} or fully deterministic like \gls{ris}, but can be semi-randomly chosen with the guidance of adaptive input state distribution, whose design incorporates the impact of information source, \gls{csi}, and \gls{qos} of both coexisting links.
		Such an adaptive backscatter channel coding boils down to the degenerate distribution of \gls{ris} when primary link is prioritized, and outperforms the conventional line coding with equiprobable inputs of \gls{bc} (by accounting the \gls{csi}) when backscatter link is prioritized.
		Besides, joint encoding over multiple co-located RIScatter nodes can further boost the total backscatter rate.
		RIScatter enables simultaneous backscatter modulation and dynamic passive beamforming, and can smoothly transition in between under different \gls{qos}.
		However, such a novel active-passive coexisting system encounters two major challenges, namely the cooperative receiver and input distribution designs.
		This is the first paper to associate \gls{bc} and \gls{ris} from a distribution perspective.
